dispRity manual

### 2017-01-06 doc/dispRity-manual.Rmd
manual updates

It is also possible to easily look at the behaviour of the disparity metric with the rarefied data (i.e. how does the disparity score change when the number of elements goes down) by using the `rarefaction = TRUE` argument:

<!-- 
```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## The rarefaction curves
plot(disp_crown_stemBS, elements = TRUE, rarefaction = TRUE)

The different dashed lines represent the different confidence intervals around each rarefaction curve. We can see that the disparity metric becomes stable after more than 10 elements.

It is also possible, when using the `type = lines` argument, to plot lines rather than boxes.
This option can be useful when displaying many series in a same window. Additionally, it is possible to plot the observed data when existing (i.e. not when the data is rarefied) by using the option `observed = TRUE`.

```{r}
## Graphical options
par(bty = "n")
## The disparity-through-time data in a time-binned way (with lines rather than
## boxes) with the observed data as crosses
plot(disp_time_binsBS, type = "lines", observed = TRUE)
```

The `type = continuous` argument plots superimposed continuous (along the x axis) polygons that represent the confidence intervals and a continuous line that represents the central tendency of the data.
Note that, as a S3 method function, `plot.dispRity` can take the classic graphical options from the `plot` function or even to add other plots to the previous ones.

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")

## First, plotting the continuous data with a y axis limit
plot(disp_time_slicesBS, type = "continuous")
## Note that the type = "continuous" argument is not mandatory here.
```

I encourage you to play with the graphical options to have some prettier results.
Note that most of the options from `plot` can be passed to `plot.dispRity` via `...`.

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## A plot with many options!
plot(disp_time_slicesBS, quantile = c(seq(from=10, to=100, by=10)),
    cent.tend = sd, type = "continuous", elements = "log",
    col = c("black", rainbow(10)), ylab = c("Disparity", "log(Diversity)"),
    xlab = "Time (in in units from past to present)", time.series = FALSE,
    observed = TRUE, main = "Many options...")
```

Finally, it is possible to add multiple plots on top of each other:

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")

## First, plotting the continuous data with a y axis limit
plot(disp_time_slicesBS, ylim = c(0.5,2))

## Second, adding the discrete data
par(new = TRUE)
plot(disp_time_binsBS, discrete_type = "line", ylim=c(0.5,2), xlab="", ylab="")
```

>>>>

Since `plot.dispRity` uses the arguments from the generic `plot` method, it is of course possible to change pretty much everything using the regular plot arguments:

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## Plotting the results with some classic options from plot
plot(disp_time_slicesBS, col = c("blue", "orange", "green"), ylab = c("Some measurement"),
    xlab = "Some other measurement", main = "Many options...", ylim = c(0,2.1))
## Adding a legend
legend("topleft", legend = c("Central tendency", "Confidence interval 1", "Confidence interval 2"),
    col = c("blue", "orange", "green"), pch = 19)
```

Additionally to the classic `plot` arguments, the function can also take arguments that are specific to `plot.dispRity` like adding the number of elements or rarefaction level (as described above) but also changing the values of the quantiles to plot as well as the central tendency.

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## Plotting the results with some plot.dispRity arguments
plot(disp_time_slicesBS, quantile = c(seq(from=10, to=100, by=10)), cent.tend = sd, type = "c",
    elements = TRUE, col = c("black", rainbow(10)), ylab = c("Disparity", "Diversity"),
    xlab = "Time (in in units from past to present)", time.series = FALSE,
    observed = TRUE, main = "Many options...")
```

> Note that the argument `observed = TRUE` allows to plot the disparity values calculated from the non-bootstrapped data as crosses on the plot.

For comparing results, it is also possible to add a plot to the existent plot by using `add = TRUE`:

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## Plotting the continuous disparity with a fixed y axis
plot(disp_time_slicesBS, ylim = c(0.5,2))
## Adding the discrete data using the same fixed y axis to have the results at the same scale
plot(disp_time_binsBS, discrete_type = "line", ylim=c(0.5,2), xlab="", ylab="", add = TRUE)
```

<!-- TODO: fix the placement bug with add = TRUE! -->

Finally, if your data has been fully rarefied, it is also possible to easily look at rarefaction curves by using the `rarefaction = TRUE` argument:

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## Plotting the rarefaction curves
plot(disp_crown_stemBS, rarefaction = TRUE)
```
<!--
